---
title: "Random Forest with stacking logged -- leaky"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, prompt=TRUE, eval=TRUE, message=F, include=T,comment=NULL,fig.width = 5, warning = FALSE, fig.height = 3,tidy.opts=list(width.cutoff=50),tidy=TRUE,cache = TRUE)
```

```{r packageCheck, include=FALSE}
mypacks <- c("tidyverse","car","tidyr","cvTools","rpart","nnet","gbm","yaImpute","randomForest", "xgboost","readr")  # what packages are needed?
packs <- installed.packages()   # find installed package list
install.me <- mypacks[!(mypacks %in% packs[,"Package"])]  #what needs to be installed?
if (length(install.me) >= 1) install.packages(install.me, repos = "http://cran.us.r-project.org")   # install (if needed)
lapply(mypacks, library, character.only=TRUE)  # load all packages
```

# Suggestion: Write functions to make this fully reproducible/easy-to-run.

# Read in help functions
```{r}
source("../help_functions/preparation&cleaning_functions.R")
source("../help_functions/modeling_functions.R")
```

# logged response

#-------------------------------------------------------
# Now start operations:

## Read in train data 
### Note: whole data train: 0.73 LB, only noleak data train: 0.72 LB
```{r}
Sys.time()
# just use only non-leaky portion to train and predict non-leaky test
# train <- read.csv("../../data/cleaned/leaky_combined_0730/train_noleak.csv")

# still use the whole "train" to train.
train <- read.csv("../../../data/raw/train.csv")

train_noid <- train %>% 
  select(-ID) %>%
  mutate(target = log(target))
Sys.time()
```

#-------------------------------------------------------
## General Cleaning: Data Quality/Unsupervised method (non-response related)

### General Cleaning (gc) step 1: get rid of invalid features (min=max)
```{r}
Sys.time()
train_gc_s1 <- noVariation_filter(train_noid)
Sys.time()
```

### General Cleaning (gc) step 2: get rid of highly correlated features
```{r}
Sys.time()
temp <- train_gc_s1 %>% select(-target)
threshold <- 0.95 # get rid of > 0.95 correlations
decorr_feas <- collinear_filter(temp, threshold)
to_select <- c(decorr_feas, "target")
train_gc_s2 <- train_gc_s1 %>% select(to_select)
Sys.time()
```

#-------------------------------------------------------
## Response-related and fit

### general initialization
```{r}
# num_top <- 100 # number of top for each round
num_top <- 300
# num_top <- 500 # updated
# num_top <- 30
train_1 <- train_gc_s2
```

### do round 1 of training fit
```{r}
num_top_1 <- num_top
cur_response_1 <- "target"
init_features_1 <- base::setdiff(names(train_1), c(cur_response_1))


train_1_small <- rf_selection(train_1, init_features_1, 
                                cur_response_1, num_top_1)
rf_best_r1 <- my_rf(train_1_small, cur_response_1)
# current r2 at this stage
mean(rf_best_r1$rsq)
```

### do round 2: fit "residuals" (stacking)
```{r}
train_2 <- train_1 %>% 
  mutate(error_r1 = target - predict(rf_best_r1)) %>%
  select(-target)

num_top_2 <- num_top
cur_response_2 <- "error_r1"

init_features_2 <- base::setdiff(names(train_2), c(cur_response_2))
# train_2_small <- corr_selection(train_2, init_features_2, 
#                                  cur_response_2, num_top_2)

train_2_small <- rf_selection(train_2, init_features_2, 
                                cur_response_2, num_top_2)

rf_best_r2 <- my_rf(train_2_small, cur_response_2)

# current r2 at this stage
mean(rf_best_r2$rsq)
```

### do round 3: fit "residuals" (stacking)
```{r}
train_3 <- train_2 %>% 
  mutate(error_r2 = error_r1 - predict(rf_best_r2)) %>%
  select(-error_r1)

num_top_3 <- num_top
cur_response_3 <- "error_r2"
init_features_3 <- base::setdiff(names(train_3), c(cur_response_3))
train_3_small <- rf_selection(train_3, init_features_3, 
                                cur_response_3, num_top_3)

rf_best_r3 <- my_rf(train_3_small, cur_response_3)
# current r2 at this stage
mean(rf_best_r3$rsq)
```

### do round 4: fit "residuals" (stacking)
```{r}
train_4 <- train_3 %>% 
  mutate(error_r3 = error_r2 - predict(rf_best_r3)) %>%
  select(-error_r2)

num_top_4 <- num_top
cur_response_4 <- "error_r3"
init_features_4 <- base::setdiff(names(train_4), c(cur_response_4))
train_4_small <- rf_selection(train_4, init_features_4, 
                                cur_response_4, num_top_4)

rf_best_r4 <- my_rf(train_4_small, cur_response_4)
# current r2 at this stage
mean(rf_best_r4$rsq)
```

```{r}
Sys.time()
```

## Read in the test set and predict
```{r}
# test <- read_csv("../../data/raw/test.csv")
test <- read_csv("../../data/cleaned/leaky_combined_0730/test_noleak.csv")
test_leaky <- read_csv("../../data/cleaned/leaky_combined_0730/test_leak.csv")
```

## let the test column match the train column
### note: if the test column starts with a number, will add an x to let it match the train columns
```{r}
all_test_col <- names(test)
all_test_col_new <- c() # new ones

for (each in all_test_col){
  each_new <- each
  
  if (is.na(as.numeric(substring(each, 1, 1))) == FALSE){ 
    # this col starts with a number
    each_new <- paste("X", each, sep = "")
  }
  all_test_col_new <- c(all_test_col_new, each_new)
  colnames(test)[which(names(test) == each)] <- each_new
}
```

## now predict stuff (for non-leaky)
```{r}
out_init <- test %>% 
  mutate(pred_m1 = predict(rf_best_r1, newdata = test),
         pred_m2 = predict(rf_best_r2, newdata = test),
         pred_m3 = predict(rf_best_r3, newdata = test),
         pred_m4 = predict(rf_best_r4, newdata = test),
         # .....
         target = pred_m1 + pred_m2 + pred_m3 + pred_m4) %>% 
        # this target needs to be exponential
  select(ID, 
         pred_m1,
         pred_m2,
         pred_m3,
         target) # for view

out <- out_init %>% 
  mutate(target = exp(target)) %>% # get the exponential
  select(-starts_with("pred"))
```

## combine with test_leaky
```{r}
test_leaky_out <- test_leaky %>% 
  select(ID, compiled_leak) %>%
  rename(target = compiled_leak)

final_out <- bind_rows(out, test_leaky_out)
```

## write out
```{r}
write.csv(final_out, 
          "../../../data/predictions/lk_predictions_rf_top300rf_stacked4_logr_trainwhole.csv", 
          row.names = FALSE)
```


```{r}

```


















