---
title: "modeling_rf_xgb_nnet_stack_log"
author: "Junxiong Liu"
date: "July 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, prompt=TRUE, eval=TRUE, message=F, include=T,comment=NULL,fig.width = 5, warning = FALSE, fig.height = 3,tidy.opts=list(width.cutoff=50),tidy=TRUE,cache = TRUE)
```

```{r packageCheck, include=FALSE}
mypacks <- c("tidyverse","car","tidyr","cvTools","rpart","nnet","gbm","yaImpute","randomForest", "xgboost","readr")  # what packages are needed?
packs <- installed.packages()   # find installed package list
install.me <- mypacks[!(mypacks %in% packs[,"Package"])]  #what needs to be installed?
if (length(install.me) >= 1) install.packages(install.me, repos = "http://cran.us.r-project.org")   # install (if needed)
lapply(mypacks, library, character.only=TRUE)  # load all packages
```

# Suggestion: Write functions to make this fully reproducible/easy-to-run.

# to be done: leaky stuff experiments get higher priority

# Read in help functions
```{r}
source("../help_functions/preparation&cleaning_functions.R")
source("../help_functions/modeling_functions.R")
```

# logged response -- stack xgboost only (vertical)

#-------------------------------------------------------
# Now start operations:

## Read in train data

### train on non-leaky: LB score 0.74
```{r}
Sys.time()

# just use only non-leaky portion to train and predict non-leaky test
train <- read.csv("../../../data/cleaned/leaky_combined_0730/train_noleak.csv")

# still use the whole "train" to train.
# train <- read.csv("../../../data/raw/train.csv")

train_noid <- train %>% 
  select(-ID) %>%
  mutate(target = log(target))
Sys.time()
```

#-------------------------------------------------------
## General Cleaning: Data Quality/Unsupervised method (non-response related)

### General Cleaning (gc) step 1: get rid of invalid features (min=max)
```{r}
Sys.time()
train_gc_s1 <- noVariation_filter(train_noid)
Sys.time()
```

### General Cleaning (gc) step 2: get rid of highly correlated features
```{r}
Sys.time()
temp <- train_gc_s1 %>% select(-target)
threshold <- 0.95 # get rid of > 0.95 correlations
decorr_feas <- collinear_filter(temp, threshold)
to_select <- c(decorr_feas, "target")
train_gc_s2 <- train_gc_s1 %>% select(to_select)
Sys.time()
```

#-------------------------------------------------------
## Response-related and fit

### general initialization
```{r}
# num_top <- 100 # number of top for each round
# num_top <- 200
num_top <- 500 # updated
# num_top <- 30
train_1 <- train_gc_s2
```

### do round 1 of training fit
```{r}
Sys.time()

# Initialize
num_top_1 <- num_top
cur_response_1 <- "target"
train_1_small <- rf_selection(train_1, init_features_1, 
                                cur_response_1, num_top_1)
init_features_1 <- base::setdiff(names(train_1_small), c(cur_response_1))

# xgboost fit
dtrain_r1 <- xgb.DMatrix(as.matrix(train_1_small[, init_features_1]), 
                         label=train_1_small[,cur_response_1])
xgb_best_r1 <- my_xgb(dtrain_r1)
dfit_r1 <- xgb.DMatrix(as.matrix(train_1_small[, init_features_1]))
Sys.time()
```

### do round 2: fit "residuals" (stacking)
```{r}
train_2 <- train_1 %>% 
  mutate(error_r1 = target - predict(xgb_best_r1, dfit_r1)) %>%
  select(-target)

# initialize for Round 2
num_top_2 <- num_top
cur_response_2 <- "error_r1"
train_2_small <- rf_selection(train_2, init_features_2, 
                                cur_response_2, num_top_2)
init_features_2 <- base::setdiff(names(train_2_small), c(cur_response_2))

# xgboost fit
dtrain_r2 <- xgb.DMatrix(as.matrix(train_2_small[, init_features_2]), 
                         label=train_2_small[,cur_response_2])
xgb_best_r2 <- my_xgb(dtrain_r2)
dfit_r2 <- xgb.DMatrix(as.matrix(train_2_small[, init_features_2]))
Sys.time()
```

### do round 3: fit "residuals" (stacking)
```{r}
train_3 <- train_2 %>% 
  mutate(error_r2 = error_r1 - predict(xgb_best_r2, dfit_r2)) %>%
  select(-error_r1)

# Initialize for Round 3
num_top_3 <- num_top
cur_response_3 <- "error_r2"
train_3_small <- rf_selection(train_3, init_features_3, 
                                cur_response_3, num_top_3)
init_features_3 <- base::setdiff(names(train_3_small), c(cur_response_3))

# xgboost fit
dtrain_r3 <- xgb.DMatrix(as.matrix(train_3_small[, init_features_3]), 
                         label=train_3_small[,cur_response_3])
xgb_best_r3 <- my_xgb(dtrain_r3)
dfit_r3 <- xgb.DMatrix(as.matrix(train_3_small[, init_features_3]))
Sys.time()
```

##----------------------------------------------------------------
## Read in the test set and predict
```{r}
test <- read_csv("../../../data/cleaned/leaky_combined_0730/test_noleak.csv")
test_leaky <- read_csv("../../../data/cleaned/leaky_combined_0730/test_leak.csv")
```

## let the test column match the train column
### note: if the test column starts with a number, will add an x to let it match the train columns
```{r}
all_test_col <- names(test)
all_test_col_new <- c() # new ones

for (each in all_test_col){
  each_new <- each
  
  if (is.na(as.numeric(substring(each, 1, 1))) == FALSE){ 
    # this col starts with a number
    each_new <- paste("X", each, sep = "")
  }
  all_test_col_new <- c(all_test_col_new, each_new)
  colnames(test)[which(names(test) == each)] <- each_new
}
```

## now predict stuff
```{r}
## for xgboost
dtest_r1 <- xgb.DMatrix(as.matrix(test[, init_features_1]))
dtest_r2 <- xgb.DMatrix(as.matrix(test[, init_features_2]))
dtest_r3 <- xgb.DMatrix(as.matrix(test[, init_features_3]))

out_init <- test %>% 
  mutate(pred_m1 = predict(xgb_best_r1, dtest_r1),
         pred_m2 = predict(xgb_best_r2, dtest_r2),
         pred_m3 = predict(xgb_best_r3, dtest_r3),
         # .....
         target = pred_m1 + pred_m2 + pred_m3) %>% 
        # this target needs to be exponential
  select(ID, 
         pred_m1,
         pred_m2,
         pred_m3,
         target) # for view

out <- out_init %>% 
  mutate(target = exp(target)) %>% # get the exponential
  select(-starts_with("pred"))
```

## combine with test_leaky
```{r}
test_leaky_out <- test_leaky %>% 
  select(ID, compiled_leak) %>%
  rename(target = compiled_leak)

final_out <- bind_rows(out, test_leaky_out)
```

## write out
```{r}
write.csv(final_out, "../../../data/predictions/lk_predictions_xgb_top500rf_stacked3_logr_trainlk.csv", 
          row.names = FALSE)
```


```{r}

```


















